%% Procedures for the Cessna 172SP
%%
%% Author:
%%   Filip Miletic (filmil@gmail.com)
%%
%% WARNING: 
%%   This was made for my personal use.  Not to be used in lieu of 
%%   actual aircraft procedures from the approved flight manual or
%%   pilot's operating handbook.

\documentclass[article,9pt,landscape]{memoir}
\usepackage{multicol,lipsum}
\usepackage[ %% Letter paper, uses almost the entire paper surface
  text={10.9in,8.3in},
  centering,ignoreall]{geometry}

\begin{document}
\input{preamble}

%%% Document titling

\begin{multicols*}{4}
  \textsc{Bay Area COM/NAV Cheat Sheet\\\today\\[0.5em]}

  \chapter{Before Taxi}
  Palo Alto Ground, Cessna 784SP\footnote{Your plane callsign.}.\\
  Advantage aviation with [alpha/bravo/\dots/]\\
  Taxi for takeoff, [right/left] departure.

  \readback
  Cessna 4SP\\
  Runway three-one\footnote{Your runway.}, taxi
  \{via the [terminal side/fuel island]\}.

  \chapter{Before Takeoff}
  Palo Alto Tower, Cessna 784SP.
  Ready for takeoff, runway three-one.

  \readback 
  Cessna 4SP, runway three-one [hold short/line up and
    wait/cleared for takeoff]

  \chapter{Entering Class D (Airport w/Tower)}
  Palo Alto tower, Cessna 784SP.
  [Leslie Salt/SLAC] with [alpha/bravo/\dots/],
  inbound for landing.

  \readback
  Cessna 4SP, make [right/left] traffic, runway three-one.

  \chapter{Before landing}
  
  \readback
  Cessna 4SP, cleared [to land/for the option], runway three-one.

  \chapter{Clear of Runway}
  Palo Alto ground, Cessna 784SP clear of the runway, taxi to
  Advantage Aviation.

  \readback
  Cessna 4SP, taxi to parking \{via parallel and Kilo\}.

  \chapter{Entering Class E/G (no tower)}
  Palo Alto traffic, Cessna 784SP [Leslie Salt/SLAC] inbound for
  landing, right traffic runway three-one, Palo Alto\footnote{Repeat
    airport name.}

  \chapter{In Pattern (no tower)}
  Palo Alto traffic, Cessna 784SP [right/left] [45/ crosswind/
    downwind/ base/ final/ short final] runway three-one, Palo Alto.

  \chapter{Class B or C}
  Norcal Approach, Cessna 784SP is a Cessna 172/Golf, VFR [altitude],
  [position], request transition of class [B/ C] airspace to
  [destination].

  \readback 
  Cessna 4SP, [route] [altitude] [cleared through the class
    B/ C] [remain clear] [maintain VFR].

  \chapter{Opening Flight Plan}
  Oakland radio, Cessna 784SP listening 122.5

  \readback
  Cessna 4SP state your request.

  \plane{Pilot} 
  Cessna 784SP, please open my VFR flight plan from Palo
  Alto to [destination], time off [10] minutes past the hour.
  
  \chapter{Bay Area Airports}

  \plane{Palo Alto Municipal (KPAO)}
  \procitem{ATIS}{135.275}
  \procitem{Tower}{118.600}
  \procitem{Ground}{125.000}
  \procitem{UNICOM}{122.850}
  \procitem{Chevron UNICOM}{122.950}
  \procitem{Elev}{4 (804E/1004W)}
  \procitem{Left traffic}{13}
  \procitem{Right traffic}{31}

  \plane{Livermore Muni (KLVK)}
  \procitem{ATIS}{119.650}
  \procitem{Tower 1}{118.100}
  \procitem{Tower 2 (sometimes in use)}{128.200}
  \procitem{Ground}{121.600}
  \procitem{UNICOM}{122.950}
  \procitem{Elev}{400 (1400)}
  \procitem{Left traffic}{7L, 25L}
  \procitem{Right traffic}{7R, 25R}
  
  \chapter{Bay Area VOR}

  \plane{Concord}
  \procitem{ID}{CCR}
  \procitem{Frequency}{117.00}
  \procitem{Morse}{\morse{-.-. -.-. .-.}}

  \plane{Manteca}
  \procitem{ID}{ECA}
  \procitem{Frequency}{116.000}
  \procitem{Morse}{\morse{. -.-. .-}}

  \plane{Oakland}
  \procitem{ID}{OAK}
  \procitem{Frequency}{116.800}
  \procitem{Morse}{\morse{--- .- -.-}}

  \plane{Point Reyes}
  \procitem{ID}{PYE}
  \procitem{Frequency}{113.700}
  \procitem{Morse}{\morse{.--. -.-- .}}
  
  \plane{San Francisco}
  \procitem{ID}{SFO}
  \procitem{Frequency}{115.800}
  \procitem{Morse}{\morse{... ..-. ---}}

  \plane{San Jose}
  \procitem{ID}{SJC}
  \procitem{Frequency}{114.100}
  \procitem{Morse}{\morse{... .--- -.-.}}

  \plane{Scaggs Island}
  \procitem{ID}{SGD}
  \procitem{Frequency}{112.10}
  \procitem{Morse}{\morse{... --. -..}}

  \plane{Sausalito}
  \procitem{ID}{SAU}
  \procitem{Frequency}{116.200}
  \procitem{Morse}{\morse{... .- ..-}}

  \plane{Woodside}
  \procitem{ID}{OSI}
  \procitem{Frequency}{113.90}
  \procitem{Morse}{\morse{--- ... ..}}

  \chapter{Bay Area Radio}

  \procitem{Oakland}{122.500}
  \procitem{International distress}{121.500}
  \procitem{NUQ DME (Moffet)}{117.600}

  \chapter{Bay Area Vectors}
  \procitem{OSI to PAO}{048 @ 9.0NM}
  \procitem{SJC to PAO}{288 @ 9.6NM}

  \input{disclaimer}
\end{multicols*}
\end{document}

%% VOR template
%% \plane{}
%% \procitem{ID}{}
%% \procitem{Frequency}{}
%% \procitem{Morse}{\morse{}}

%% RWY template
%% \plane{ ()}
%% \procitem{ATIS}{}
%% \procitem{Tower}{}
%% \procitem{Ground}{}
%% \procitem{UNICOM}{}
%% \procitem{Elev}{4 ()}
%% \procitem{Left traffic}{}
%% \procitem{Right traffic}{}
